---
title: "Gapminder Analysis"
author: "Sola Takahashi"
date: "2024-02-07"
output: 
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide 
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the first line of my document. In this document, I will analyze how life expectancy has changed over time.

# Reading in gapminder data

```{r reading_in_data}
 gapminder_df <- read.csv("data/gapminder_data.csv")

#getwd()
```

## A smaller header

### An even smaller header

##### A very small header

lists:

-   list item 1
-   list item 2

Another type of list:

-   Hyphen list
-   Hyphen list

Numbers lists:

1.  Number one
2.  Number two
    -   Sub list
3.  Number three

Test if we need a space:

-   Test list one
-   Test list two

We make text **bold with two asterisks** or *italic with one asterisk*

We can also insert Greek letters $\mu$ or $\Delta$

We can make [hyperlinks](https://pad.carpentries.org/Spring2024-BIOMI6300)

# Calculating summary statistics

```{R calculatng_median_pop, echo = FALSE}
 med_pop <- median(gapminder_df$pop)

 num_obs <- nrow(gapminder_df)
```

Over `r num_obs` observations, the median population was `r round(med_pop/10e6, 3)` million people.

# Plotting Life Expectancy Over the Years

```{r line_graph, warning = FALSE}
library(ggplot2) 

ggplot(gapminder_df,aes(x =year, y = lifeExp, group = country, color = continent)) +
  geom_line() +
  scale_y_log10() +
  scale_x_continuous(limits = c(1997, 2007)) #get a warning message that you removed data 
```

# Plotting Population Distribution

```{r histogram, message = FALSE, fig.width = 10}
ggplot(gapminder_df, aes(x = pop)) +
  geom_histogram()
```

| Col1 | Col2 | Col3 |
|------|------|------|
|      |      |      |
|      |      |      |
|      |      |      |

And we add some new lines because now we're working on git.
